\phantomsection
\addcontentsline{toc}{section}{参考文献}
\begin{thebibliography}{99}

\bibitem{yayi2016super}
韦亚一.
\CJKtextit{超大规模集成电路先进光刻理论与应用}.
北京: 科学出版社, 2016.

\bibitem{adel2008diffraction}
Mike Adel, Daniel Kandel, Vladimir Levinski, Joel Seligson and Alex Kuniavsky.
\textit{Diffraction order control in overlay metrology -- a review of the roadmap options}.
Metrology, Inspection, and Process Control for Microlithography XXIX, Proceedings Vol. \textbf{6922}: 692202, 2008.

\bibitem{qiang2020diffraction}
伍强~等编著.
\CJKtextit{衍射极限附近的光刻工艺}.
北京: 清华大学出版社, 2020.

\bibitem{blancquaert2013diffraction}
Yoann Blancquaert and Christophe Dezauzier.
\textit{Diffraction based overlay and image based overlay on production flow for advanced technology node}.
Metrology, Inspection, and Process Control for Microlithography XXVII, Proceedings Vol. \textbf{8681}: 86812O, 2013.

\bibitem{swinkels2021spectral}
Daan Swinkels.
\textit{Spectral shaping for the next-generation overlay metrology}.
Student thesis: Master, 2021.

\bibitem{sohn2006kohler}
Yeung Joon Sohn, Bryan M. Barnes, Lowell Howard, Richard M. Silver, Ravikiran Attota and Michael T. Stocker.
\textit{K\'{o}hler Illumination for High-resolution Optical Metrolog}.
Metrology, Inspection, and Process Control for Microlithography X, Proceedings Vol. \textbf{6152}: 61523S, 2006.

\bibitem{hsieh2023designing}
Hung-Chih Hsieh, Meng-Rong Wu and Xiang-Ting Huang.
\textit{Designing highly precise overlay targets for asymmetric sidewall structures using quasi-periodic line widths and finite-difference time-domain simulation}.
Sensors \textbf{23}: 4482, 2023.

\bibitem{goodman1996introduction}
Joseph W. Goodman.
\textit{Introduction to Fourier optics.}.
Roberts \& Co., Englewood, Colo, 2nd edition, 1996.




%\bibitem{merton1972an}
%Robert C. Merton.
%\textit{An analytic derivation of the efficient portfolio frontier}.
%The Journal of Financial and Quantitative Analysis \textbf{7}:1851-1872, 1972.


% \bibitem{descartes1637discours}
% Ren\'{e} Descartes.
% \textit{Discours de la M\'{e}thode}, 1637.


% \bibitem{random-forest-classifier}
% Random Forest Classifier. \\
% \url{https://scikit-learn.org/stable/modules/generated/sklearn.ensemble.RandomForestClassifier.html}.

\end{thebibliography}